---
title: "Lab10"
author: "Chen Chen 6381370662"
date: "`r Sys.Date()`"
output: 
   github_document
always_allow_html: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(repos = c(CRAN = "http://cran.rstudio.com"))
```


```{r}
# install.packages(c("RSQLite", "DBI"))
if(!require(RSQLite))install.packages(c("RSQLite"))
if(!require(DBI))install.packages(c("DBI"))
library(RSQLite)
library(DBI)
```


#Data setup
```{r}
# Initialize a temporary in memory database
con <- dbConnect(SQLite(), ":memory:")

# Download tables
actor <- read.csv("https://raw.githubusercontent.com/ivanceras/sakila/master/csv-sakila-db/actor.csv")
rental <- read.csv("https://raw.githubusercontent.com/ivanceras/sakila/master/csv-sakila-db/rental.csv")
customer <- read.csv("https://raw.githubusercontent.com/ivanceras/sakila/master/csv-sakila-db/customer.csv")
payment <- read.csv("https://raw.githubusercontent.com/ivanceras/sakila/master/csv-sakila-db/payment_p2007_01.csv")

# Copy data.frames to database
dbWriteTable(con, "actor", actor)
dbWriteTable(con, "rental", rental)
dbWriteTable(con, "customer", customer)
dbWriteTable(con, "payment", payment)
dbListTables(con)
```

```{sql, connection= con}
PRAGMA table_info(actor)
```

Exercise 1
Retrieve the actor ID, first name and last name for all actors using the actor table. Sort by last name and then by first name.

```{r}
dbGetQuery(con, "
           SELECT  actor_id, first_name, last_name
           FROM    actor
           ORDER by last_name, first_name
           ")
```
Try in SQL directly:
```{sql, connection= con}
 SELECT  actor_id, first_name, last_name
           FROM    actor
           ORDER by last_name, first_name
```

#Exercise 2
Retrieve the actor ID, first name, and last name for actors whose last name equals ‘WILLIAMS’ or ‘DAVIS’.

```{r}
dbGetQuery(con, "
SELECT actor_id, first_name, last_name
FROM actor
WHERE last_name IN ('WILLIAMS', 'DAVIS')
ORDER BY last_name
")
```
##Exercise 3
Write a query against the rental table that returns the IDs of the customers who rented a film on July 5, 2005 (use the rental.rental_date column, and you can use the date() function to ignore the time component). Include a single row for each distinct customer ID.

```{r}
dbGetQuery(con, "
SELECT DISTINCT customer_id, rental_date
FROM  rental
WHERE date(rental_date) = '2005-07-05'
")
```
```{r}

dbGetQuery(con, "
SELECT customer_id,
  COUNT(*) as N
FROM rental
WHERE date(rental_date) = '2005-07-05'
GROUP BY customer_id
")
```
#Exercise 4
Construct a query that retries all rows from the payment table where the amount is either 1.99, 7.99, 9.99.

```{r}
dbGetQuery(con,"
SELECT *
FROM payment
WHERE amount IN (1.99, 7.99, 9.99)  
LIMIT 10
           ")
```

Construct a query that retrieve all rows from the payment table where the amount is greater then 5

```{r}
dbGetQuery(con,"
SELECT *
FROM payment
WHERE amount > 5
LIMIT 10
")
```
Construct a query that retrives all rows from the payment table where the amount is greater then 5 and less then 8
```{r}
dbGetQuery(con,"
SELECT *
FROM payment
WHERE amount > 5 AND amount<8
LIMIT 10
")
```
#Exercise 5
Retrieve all the payment IDs and their amount from the customers whose last name is ‘DAVIS’.

```{sql, connection= con}
PRAGMA table_info(customer)
```

```{r}
dbGetQuery(con,"
SELECT c.customer_id, p.payment_id, p.amount, c.last_name
FROM customer AS c INNER JOIN payment AS p
ON c.customer_id = p.customer_id
WHERE c.last_name =='DAVIS'
/* This is a comment*/
")
```

#Exercise 6

Use COUNT(*) to count the number of rows in rental
```{r}
dbGetQuery(con,"
SELECT COUNT(*) AS count
From rental
")
```

Use COUNT(*) and GROUP BY to count the number of rentals for each customer_id
```{r}
dbGetQuery(con,"
SELECT customer_id, COUNT(*) AS count
From rental
GROUP BY customer_id
LIMIT 8
")
```

Repeat the previous query and sort by the count in descending order
```{r}
dbGetQuery(con,"
SELECT customer_id, COUNT(*) AS count
From rental
GROUP BY customer_id
ORDER BY count DESC
LIMIT 8
")
```

Repeat the previous query but use HAVING to only keep the groups with 40 or more.
```{r}
dbGetQuery(con,"
SELECT customer_id, COUNT(*) AS count
From rental
GROUP BY customer_id
HAVING count > 40
ORDER BY count DESC
LIMIT 8
")
```

#Exercise 7
The following query calculates a number of summary statistics for the payment table using MAX, MIN, AVG and SUM
Modify the above query to do those calculations for each customer_id
```{r}
dbGetQuery(con,"
SELECT customer_id,
       MAX(amount) AS maxpayment,
       MIN(amount) AS minpayment,
       AVG(amount) AS avgpayment,
       SUM(amount) AS sunpayment
FROM payment
GROUP BY customer_id
LIMIT 5
")
```

Modify the above query to only keep the customer_ids that have more then 5 payments
```{r}
dbGetQuery(con,"
SELECT COUNT(*) AS N,
       customer_id,
       MAX(amount) AS maxpayment,
       MIN(amount) AS minpayment,
       AVG(amount) AS avgpayment,
       SUM(amount) AS sunpayment
FROM payment
GROUP BY customer_id
HAVING N>5
")
```


#clean up
```{r}
dbDisconnect(con)
```

