---
title: "Lab4"
author: "Chen Chen 6381370662"
date: "`r Sys.Date()`"
output: github_document
always_allow_html: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r install-library}
library(lubridate)
library(tidyverse)
library(data.table)
```

## Step 1. Read in the data
First download and then read in with data.table:fread()

```{r}
if (!file.exists("../lab3/met_all.gz")){
  download.file("https://raw.githubusercontent.com/USCbiostats/data-science-data/master/02_met/met_all.gz", "met_all.gz", method="libcurl", timeout = 60)
}
met <- data.table::fread("../lab3/met_all.gz")
```


## Step 2. Prep Data

Remove temperatures less than -17C and change elev 9999 to missing value code.
```{r remove-low-temp}
met <- met[temp > -17][elev == 9999.0, elev:= NA]
```

Make sure there are no missing data in the key variables coded as 9999, 999, etc
```{r}
met[met$elev==9999.0] <- NA
summary(met$elev)
```

Generate a date variable using the functions as.Date() (hint: You will need the following to create a date paste(year, month, day, sep = "-")).
```{r}
met <- met[ , ymd:= as.Date(paste(year, month, day, sep = "-"))]
```

Using the data.table::week function, keep the observations of the first week of the month.
```{r}
met[, table(week(ymd))]
met <- met[week(ymd)==31]
```

Compute the mean by station of the variables temp, rh, wind.sp, vis.dist, dew.point, lat, lon, and elev.
```{r check-max}
 met[ , .(
  temp     = max(temp,na.rm=T),
  rh       = max(rh, na.rm=T),
  wind.sp  = max(wind.sp, na.rm=T),
  vis.dist =max(vis.dist, na.rm=T),
  dew.point=max(dew.point, na.rm=T),
  lat      =max(lat, na.rm=T),
  lon      =max(lon, na.rm=T),
  elev     =max(elev, na.rm=T)
)]
```

```{r}
met_avg <- met[ , .(
  temp=mean(temp, na.rm=T),
  rh= mean(rh, na.rm=T),
  wind.sp= mean(wind.sp, na.rm=T),
  vis.dist =mean(vis.dist, na.rm=T),
  dew.point=mean(dew.point, na.rm=T),
  lat=mean(lat, na.rm=T),
  lon=mean(lon, na.rm=T),
  elev=mean(elev, na.rm=T)
), by = "USAFID"]
```

```{r}

```


Create a region variable for NW, SW, NE, SE based on lon = -98.00 and lat = 39.71 degrees
Create a categorical variable for elevation as in the lecture slides

```{r}

```

```{r}

```

```{r}

```

```{r}

```

