---
title: "Lab3"
author: "Chen Chen 6381370662"
date: "`r Sys.Date()`"
output: github_document
always_allow_html: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Step 1. Read in the data
First download and then read in with data.table:fread()

```{r}
if (!file.exists("met_all.gz")){
  download.file("https://raw.githubusercontent.com/USCbiostats/data-science-data/master/02_met/met_all.gz", "met_all.gz", method="libcurl", timeout = 60)
}
met <- data.table::fread("met_all.gz")
```


## Step 2. Check the dimensions, headers, footers. How many columns, rows are there?


```{r}
dim(met)
head(met)
tail(met)
```

## Step 3. Take a look at the variables.

```{r}
str(met)
```

## Step 4. Take a closer look at the key variables.
```{r}
table(met$year)
```

```{r}
table(met$day)
```

```{r}
table(met$hour)
```

```{r}
summary(met$temp)
summary(met$elev)
summary(met$wind.sp)
```

## Replace elevations with 9999 as NA.
```{r}
met[met$elev==9999.0] <- NA
summary(met$elev)
```
 
 The weather station with the highest elevation is at `r max(met$elev, na.rm=TRUE) ` meters.
 
Remove temps below -40 Celsius.
 
```{r}
met <- met[temp>-40][order(temp)]
```
 
## Step 5. Check the data against an external data source.
```{r}
met <- met[temp>-15][order(temp)]
```

 
## Step 6. Compute summary statistics
```{r}
met[elev==max(elev, na.rm=TRUE), summary(wind.sp)]
met[elev==max(elev, na.rm=TRUE), summary(temp)]
```

```{r}
met[elev==max(elev, na.rm=TRUE), .(
  temp_wind    = cor(temp, wind.sp, use="complete"),
  temp_hour    = cor(temp, hour, use="complete"),
  wind.sp_day  = cor(wind.sp, day, use="complete"),
  wind.sp_hour = cor(wind.sp, hour, use="complete")  
)]
```

## Step 7. Exploratory Graphs

```{r}
hist(met$elev, breaks=100)
```
```{r}
hist(met$temp)
```

```{r}
hist(met$wind.sp)
```
```{r}
library(leaflet)
elev <- met[elev==max(elev)]
```

```{r}
leaflet(elev) %>%
  addProviderTiles('OpenStreetMap') %>% 
  addCircles(lat=~lat,lng=~lon, opacity=1, fillOpacity=1, radius=100)
```

```{r}
library(lubridate)
elev$date <- with(elev, ymd_h(paste(year, month, day, hour, sep= ' ')))
summary(elev$date)
```
```{r}
elev <- elev[order(date)]
head(elev)
```


```{r}
plot(elev$date, elev$temp, type='l')
```
```{r}
plot(elev$date, elev$wind.sp, type='l')
```


